Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-30 reviews.Rmd
Update reviews.Rmd

Neither is severity as an absolute measure of corroboration a common consideration in empirical psychological work.
However, the posterior probability is certainly the most classic measure of absolute confirmation in the philosophy of science.

@@

> In fact, it is entirely possible to assume the null hypothesis as a research hypothesis, as is commonly done in e.g., structural equation modelling, where the roles of detectability, theoretical risk and type-I/II error rate switch.

@@

Perhaps, we are a bit daft but a clear definition of error rate control eludes us.
We are under the impression that two competing definitions are used here from time to time.
First, a definition in which control means the error rates are known (but then known by whom?).
Second, control means ensuring certain acceptable bounds of error rates are not exceeded.

>>>>

Neither is severity -- as an absolute measure of corroboration -- a common consideration in empirical psychological work.
However, the posterior probability is certainly the most classic measure of absolute confirmation in the philosophy of science.

@@

> In fact, it is entirely possible to assume the null hypothesis as a research hypothesis, as is commonly done in e.g., structural equation modelling.
Then, the roles of detectability, theoretical risk and type-I/II error rate switch, yet our line of reasoning stays the same.

@@

We are under the impression that two inconsistent definitions of *control* of error rates are used by the reviewer.
First, a definition in which control means the error rates are known (but then known by whom?).
Second, control means ensuring certain acceptable bounds of error rates are not exceeded.
